On the effects of partying on next-day sports performance

### 2017-07-12 writing/draft.tex
Updated table on Team Points Allowed/Scored.

\begin{figure}
%\includegraphics[scale=0.5]{travel_dist_by_party}
  \centering
  \includegraphics[scale=0.55]{travel_dist_density_by_party}
  \label{fig: density by party}
  \caption{Within the NBA, we examine travel distance to current game location as a function of
    whether the last game was in a (non) party city. We see that in general,
  travel distance follows a similar distribution regardless of last game location, i.e. 
  it's not as though players encounter significantly
  more travel fatigue after playing in a party city. We mention that the same plot is not interesting to look at within the MLB, since games are played in series, and therefore most travel-distances between games are zero miles.}
\end{figure}

@@

% mpa1, tpa, tpo
\hspace{-125pt}
\begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & Team Points Admitted & Team Points Admitted & Team Points Scored \\  \\[-1.8ex] & (1) & (2) & (3)\\  \hline \\[-1.8ex]   Discrete party indicator & 2.649$^{***}$ &  &  \\    & (0.718) &  &  \\    & & & \\   Continuous party measure &  & 1.833$^{***}$ & 0.447$^{*}$ \\    &  & (0.246) & (0.245) \\    & & & \\   Lag change in possessions & 1.058$^{*}$ & 0.022$^{***}$ & 0.035$^{***}$ \\    & (0.615) & (0.007) & (0.007) \\    & & & \\   Logged travel distance & $-$0.045 & $-$0.028 & $-$0.213$^{***}$ \\    & (0.038) & (0.074) & (0.074) \\    & & & \\   Number hours since last game & 0.009$^{**}$ & 0.015$^{***}$ & 0.018$^{***}$ \\    & (0.004) & (0.003) & (0.003) \\    & & & \\   Home team effect & $-$2.997$^{***}$ & $-$3.412$^{***}$ & 2.211$^{***}$ \\    & (0.218) & (0.116) & (0.116) \\    & & & \\   Constant & $-$3.429 & 101.941$^{***}$ & 100.112$^{***}$ \\    & (2.926) & (0.479) & (0.477) \\    & & & \\  \hline \\[-1.8ex]  Observations & 14,843 & 44,689 & 44,689 \\  R$^{2}$ & 0.018 & 0.021 & 0.010 \\  Adjusted R$^{2}$ & 0.017 & 0.021 & 0.010 \\  Residual Std. Error & 11.070 (df = 14831) & 12.002 (df = 44683) & 11.967 (df = 44683) \\  F Statistic & 24.021$^{***}$ (df = 11; 14831) & 196.086$^{***}$ (df = 5; 44683) & 92.809$^{***}$ (df = 5; 44683) \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}    
\section{Conclusions and Avenues for Future Research}
\subsection{Extending the research}
\paragraph{Within the NBA} 
We're interested to explore what other factors may affect a team's propensity to suffer hangover effects beyond simply visiting a party city; e.g. are teams more likely to go out after
a win or a loss? Do teams who aren't going to make the playoffs party more? Are there demographic
factors which influence partying, e.g. are younger, unmarried players more susceptible to treatment effect? Within a game, it would be interesting to look at 
number of shots taken, and number of shots taken by 
stars as a function of previous day visitation to party cities. We could also investigate 
effects on injury risk and flagrant foul rates.

>>>>

\begin{figure}
%\includegraphics[scale=0.5]{travel_dist_by_party}
  \centering
  \includegraphics[scale=0.425]{travel_dist_density_by_party}
  \label{fig: density by party}
  \caption{Within the NBA, we examine travel distance to current game location as a function of
    whether the last game was in a (non) party city. We see that in general,
    when traveling from a non party-oriented city to next game location, the distribution
    of travel-distance has fatter tails. This makes sense: as we saw in our previous
    heat-map, next day opponent geographically correlated with current game location.
    Since LA and NY are on the coast, their next day opponent is likely to be nearby; compare
    this to inland cities, for example, who may have to travel farther to reach their 
    nearest neighbor. We mention that the same     plot is not interesting to look at within the MLB, since games are played in     series, and therefore most travel-distances between games are zero miles.}
\end{figure}

@@

% mpa1, tpa, tpo
\hspace{-35pt}
\begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & \multicolumn{2}{c}{Team Points Admitted} & Team Points Scored \\  \\[-1.8ex] & (1) & (2) & (3)\\  \hline \\[-1.8ex]   Discrete party indicator & 2.970$^{***}$ &  &  \\    & (0.835) &  &  \\    & & & \\   Continuous party measure &  & 1.661$^{***}$ & $-$0.139 \\    &  & (0.644) & (0.637) \\    & & & \\   Lag change in possessions & 6.694$^{***}$ & 6.751$^{***}$ & 5.858$^{***}$ \\    & (0.973) & (0.973) & (0.963) \\    & & & \\   Logged travel distance & $-$0.114 & $-$0.132 & $-$0.285 \\    & (0.198) & (0.198) & (0.196) \\    & & & \\   Number hours since last game & 0.011$^{*}$ & 0.015$^{**}$ & 0.016$^{**}$ \\    & (0.006) & (0.007) & (0.007) \\    & & & \\   Home team effect & $-$3.269$^{***}$ & $-$3.269$^{***}$ & 2.417$^{***}$ \\    & (0.303) & (0.303) & (0.300) \\    & & & \\   Constant & 68.114$^{***}$ & 67.686$^{***}$ & 71.348$^{***}$ \\    & (4.805) & (4.810) & (4.758) \\    & & & \\  \hline \\[-1.8ex]  Observations & 6,234 & 6,234 & 6,234 \\  R$^{2}$ & 0.091 & 0.090 & 0.084 \\  Adjusted R$^{2}$ & 0.087 & 0.086 & 0.079 \\  Residual Std. Error (df = 6201) & 11.670 & 11.675 & 11.549 \\  F Statistic (df = 32; 6201) & 19.453$^{***}$ & 19.247$^{***}$ & 17.720$^{***}$ \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  
\section{Conclusions and Avenues for Future Research}
\subsection{Extending the research}
\paragraph{Within the NBA} 
We're interested to explore what other factors may affect a team's propensity to suffer hangover effects beyond simply visiting a party city; e.g. are teams more likely to go out after
a win or a loss? Do teams who aren't going to make the playoffs party more? Are there demographic
factors which influence partying, e.g. are younger, unmarried players more susceptible to treatment effect? Within a game, it would be interesting to look at 
number of shots taken, and number of shots taken by 
stars as a function of previous day visitation to party cities. We could also investigate 
effects on injury risk and flagrant foul rates.
